---
title: "Assignment 9"
author: "Alena Oxenham"
date: "4/3/2022"
output: html_document
---

Part 1

Earlier in the semester, we discussed what workflows look like. Since then, we’ve spent approximately 8 weeks using R and thinking about other aspects of the course. Based on what you’ve learned, create a workflow for analyzing data.

Part 2

In this section of the assignment, I will ask you to work through making your own workflow and practice using some of the tools we’ve discussed.

Create an R project for this assignment.
Inside this R project, place a .csv file that contains a column of your five favorite desserts, a column of the rating you’d give the dessert, and a third column containing roughly the quantity of said dessert you could eat.
Create an R Markdown file in the R project that 
1) uploads the data, 
```{r}
dat<-Dessert_Data
```

2) summarizes the three columns, and 
```{r}
library(haven)
library(ggplot2)

summary(dat$Rating)
summary(dat$Quantity)
dat$Dessert
```
3) visually represents the data in some way.
```{r}
ggplot(dat, aes(Rating,Quantity))+geom_point()+facet_wrap(~Dessert)+theme_minimal()
```
Create your own repository of this Project on GitHub and paste a link to your repository here.
Link: https://github.com/afoxenham/Assignment-9
Generate a readme file to help me figure out what you’ve done :)
